Historical Methods 1640-1828

### 2018-08-31 inst/examples/201808-HistoricalMethods-Overview.Rmd
ok

@@

Number of unique and all genres per catalogue.

@@

The most common genres in Fennica:

```{r genres_fen, echo=FALSE, message=FALSE, warning=FALSE}
kable(top(fen, "Subject", 10, "data.frame"), digits = 1)
```

The most common genres in Kungliga:

```{r genres_kun, echo=FALSE, message=FALSE, warning=FALSE}
kable(top(kun, "Subject", 10, "data.frame"), digits = 1)
```

@@

```{r publishers_fen, echo=FALSE, message=FALSE, warning=FALSE}
kable(top(fen, field, 10, "data.frame"), digits = 1)
```

@@

```{r publishers_kun, echo=FALSE, message=FALSE, warning=FALSE}
kable(top(kun, field, 10, "data.frame"), digits = 1)
```

@@

```{r authors_fen, echo=FALSE, message=FALSE, warning=FALSE}
kable(top(fen, field, 10, "data.frame"), digits = 1)
```

@@

```{r authors_kun, echo=FALSE, message=FALSE, warning=FALSE}
kable(top(kun, field, 10, "data.frame"), digits = 1)
```

@@

```{r languages_fen, echo=FALSE, message=FALSE, warning=FALSE}
kable(top(fen, field, 10, "data.frame"), digits = 1)
```

@@

```{r languages_kun, echo=FALSE, message=FALSE, warning=FALSE}
kable(top(kun, field, 10, "data.frame"), digits = 1)
```

@@

```{r places_fen, echo=FALSE, message=FALSE, warning=FALSE}
kable(top(fen, field, 10, "data.frame"), digits = 1)
```

@@

```{r places_kun, echo=FALSE, message=FALSE, warning=FALSE}
kable(top(kun, field, 10, "data.frame"), digits = 1)
```

>>>>

selected.fields <- c("publication_year", "publication_place", "gatherings", "title", "pagecount", "publisher", "language", "Subject")

@@

Number of unique and all subject topics per catalogue.

@@

The most common subject topics in Fennica:

```{r genres_fen, echo=FALSE, message=FALSE, warning=FALSE}
kable(top(fen, "Subject", 10, "data.frame", round = 1))
```

The most common subject topics in Kungliga:

```{r genres_kun, echo=FALSE, message=FALSE, warning=FALSE}
kable(top(kun, "Subject", 10, "data.frame", round = 1))
```

@@

```{r publishers_fen, echo=FALSE, message=FALSE, warning=FALSE}
kable(top(fen, field, 10, "data.frame", round = 1))
```

@@

```{r publishers_kun, echo=FALSE, message=FALSE, warning=FALSE}
kable(top(kun, field, 10, "data.frame", round = 1))
```

@@

```{r authors_fen, echo=FALSE, message=FALSE, warning=FALSE}
kable(top(fen, field, 10, "data.frame", round = 1))
```

@@

```{r authors_kun, echo=FALSE, message=FALSE, warning=FALSE}
kable(top(kun, field, 10, "data.frame", round = 1))
```

@@

```{r languages_fen, echo=FALSE, message=FALSE, warning=FALSE}
kable(top(fen, field, 10, "data.frame", round = 1))
```

@@

```{r languages_kun, echo=FALSE, message=FALSE, warning=FALSE}
kable(top(kun, field, 10, "data.frame", round = 1))
```

@@

```{r places_fen, echo=FALSE, message=FALSE, warning=FALSE}
kable(top(fen, field, 10, "data.frame", round = 1))
```

@@

```{r places_kun, echo=FALSE, message=FALSE, warning=FALSE}
kable(top(kun, field, 10, "data.frame", round = 1))
```
